Meeting the Challenges of Modeling Astrophysical Thermonuclear Explosions: \castro, \maestro, and the \amrex\ Astrophysics Suite

### 2017-10-24 astronum_2017/astronum-amrex.tex
address Chris's marginpar

\castro\ has been applied to core-collapse
supernovae~\cite{castro-ccsne}, population III pair-instability
supernovae~\cite{castro-pairinstability}, and white dwarf mergers as a
model for SNe Ia~\cite{wdmergerI}.  Recent work has focused on
improving energy conservation with gravitational and rotational
sources, and new integration methods that more accurately couple hydro
and reactions.  For \maestro\ simulations that evolve from the
subsonic regime to the sonic regime, we have demonstrated the ability
to restart the calculations in \castro\ to continue the evolution into
the sonic regime~\cite{scidac-petascale,malone:2014} (in this case,
for Chandra model SNe Ia).

>>>>

\castro\ has been applied to core-collapse
supernovae~\cite{castro-ccsne}, radiative shock breakout in
supernovae~\cite{lovegrove:2017}, population III pair-instability
supernovae~\cite{castro-pairinstability}, the Chandra model for
SNe~Ia~\cite{ma:2013}, the sub-Chandra SNe Ia model~\cite{moll:2013}, and white dwarf mergers as a model for SNe
Ia~\cite{moll:2014,wdmergerI}. Recent work has focused on improving energy
conservation with gravitational and rotational sources, and new
integration methods that more accurately couple hydro and reactions.
For \maestro\ simulations that evolve from the subsonic regime to the
sonic regime, we have demonstrated the ability to restart the
calculations in \castro\ to continue the evolution into the sonic
regime~\cite{scidac-petascale,malone:2014} (in this case, for Chandra
model SNe Ia).
